---
title: "twfyR"
author: Jack Blumenau
output: github_document
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "##",
  fig.path = "images/"
)
library(twfyR)
```

## About the package

This package provides an R binding for the [TheyWorkForYou API](http://www.theyWorkForYou.com/api). This package is still in the very early stages of development. Use with caution.

## How to install

The package is currently only available on github.

```{eval = F}
library(devtools)
install_github("jblumenau/twfyR")
library(twfyR)
```

## Set your API key

Use of the API is dependent on obtaining an API key from TheyWorkForYou. This is easily done [here](https://www.theyworkforyou.com/api/key).

Before trying to get any data using the R functions in this package, you will need to use the `set_twfy_key()` function.

```{r key_example, eval = F}
my_key <- "api_key_from_twfy"
set_twfy_key(my_key)
```

```{r key_example2, eval = T, message=FALSE, echo=FALSE}
my_key <- "api_key_from_twfy"
set_twfy_key(my_key)
```

## Calling the API

Calls to the twfy API are made via a series of `get` functions, such as `getMPs()` and `getDebates()`. Note that currently the package is incomplete in various ways, the most notable of which is that it does not yet include bindings for all of the calls made available by TWFY. Hopefully these will be added in the not-too-distant future...

Each of these functions takes a number of arguments to refine the results that are returned by the API. In each case, the function attempts to convert the XML data returned by the call into an R data object (normally a `data.frame` but sometimes a `list` (and sometimes even a `list` of `data.frames`)).

Let's try getting the current MPs serving in parliament. This is the default output of the `getMPs()` function:

```{r get_mps, eval = T, warning=FALSE, cache=TRUE}
current_mps <- getMPs()

str(current_mps)
```

The output is a list of 2 `data.frames`. The first is a data.frame with unique rows for each current MP. The second is a data.frame of each parliamentary position that each current member holds.

Let's try retreiving the speeches of one member of parliament. We'll use the `getDebates()` function, and use `type = "commons"` to specify that we wish to see speeches made in the House of Commons, and `person = 10001` to choose our MP of interest (here it is [Dianne Abbott](https://www.theyworkforyou.com/mp/10001/diane_abbott/hackney_north_and_stoke_newington)).

```{r get_debates, eval = T, warning=FALSE, cache=TRUE}
speeches <- getDebates(person = 10001, type = "commons")

class(speeches)

dim(speeches)
```

The default behaviour of the `getDebates()` function is to return 1000 results. But if we wish to receive *all* the speeches ever made by a given person, we can set `complete_call = TRUE`. Note, however, that this specification will submit several requests to the twfy API, and is a quick way to use up your call allowance if done too often.

Finally, let's do something with these speeches using the excellent [quanteda](https://github.com/kbenoit/quanteda) library.

```{r wordcloud, eval = T, warning=FALSE, cache=TRUE, message=FALSE}
library(quanteda)

speech_corpus <- corpus(speeches$body)

speech_dfm <- dfm(speech_corpus, remove = c("will", stopwords("english")),
             removePunct = TRUE)

speech_dfm <- dfm_trim(speech_dfm, max_count = 400, min_count = 10)

speech_idf <- tfidf(speech_dfm)

textplot_wordcloud(speech_idf, min.req = 10, random.order = FALSE, rot.per = .25, 
                   colors = RColorBrewer::brewer.pal(8,"Dark2"))
```